---
title: "SAP Materials MPN matching from Utopia and Spare Parts Followup"
author: "Pascal Bellerose"
date: "02/12/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("https://raw.githubusercontent.com/FireFighter1017/COEMF/master/funcs/lubripack.r")
source("https://raw.githubusercontent.com/FireFighter1017/COEMF_MPN/master/scripts/mm_readCleanUtopia.r")
source("https://raw.githubusercontent.com/FireFighter1017/COEMF_MPN/master/scripts/mm_readCleanSPF.r")
source("https://raw.githubusercontent.com/FireFighter1017/COEMF/master/MasterData/funcs/normVendor.r")
source("https://raw.githubusercontent.com/FireFighter1017/COEMF_MPN/master/scripts/UtopiaStats.r")
source("https://raw.githubusercontent.com/FireFighter1017/COEMF_MPN/master/scripts/mm_matchToZ011.r")

```


## Input files statistics

### Cascades Spare Parts Followup (OU_00065)

This file was created for the sole purpose of storing the MPN information in a structured way, to prevent the need for MPN extraction from the description.  This process started at SAP Part# `90012072` with the MRO project for plants 3411 and 2241.  

```{r loadSPFData, echo=FALSE, warning=FALSE, message=FALSE}
  ## Read Spare Parts Followup Data
  SPF <- readCleanSPF()
  nSPF <- nrow(SPF)
  lowSPF <- min(as.numeric(SPF[,6]))
  hiSPF <- max(as.numeric(SPF[,6]))
```

Number of valid records in OU_00065: `r print(nSPF)`
Lowest material number : `r print(lowSPF)`
highest material number : `r print(hiSPF)`

### Utopia

This file is a list of materials for which the company Utopia inc. has extracted the MPN information from the description when possible.  

```{r loadUtopiaData, include=FALSE}
  ## Read Utopia Data
  Utopia <- readCleanUtopia()
```

The file name: *Cascades_Master_File_20181029_V1.xlsx*

```{r UtopiaStats, echo=FALSE, warning=FALSE, message=FALSE, results='markup'}
  print(paste("Number of valid records in Utopia : ",
            nrow(Utopia),
            sep="")
        )
  UtopiaStats(Utopia)  
```


